\texttt{dispRity} demo for ecologists

### 2015-11-30 doc/dispRity-ecology-demo.Rnw
minor update (install.package)

<<installation, eval=FALSE>>=
install.packages("devtools")
library(devtools)
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)
@

>>>>

<<installation, eval=FALSE>>=
if(!require(devtools)) install.packages("devtools")
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)
@
